Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-04-13 ltx/BrainIDE.tex
added to freq analysis in paper

The spectral characteristics of the field are governed by the the shape of the connectivity kernel or the coloring of the covariance of the field disturbance. If the bandwidth of the disturbance covariance was greater than the bandwidth of the connectivity kernel than the disturbance governs the bandwidth of the system. Conversely, if the bandwidth of the kernel was higher then it will govern the systems bandwidth. Note, the observable characteristics of the kernel are governed by how it is excited by the input.

Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited. Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}. In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field. Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually bandlimited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$. Given such a bandlimited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$. Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.

Sensors act as a low-pass filter

>>>>

The spectral characteristics of the field are governed by the the shape of the connectivity kernel or the coloring of the covariance of the field disturbance. If the bandwidth of the disturbance covariance was greater than the bandwidth of the connectivity kernel than the disturbance governs the bandwidth of the system. Conversely, if the bandwidth of the kernel was higher then it will govern the systems bandwidth. Note, the theoretically observable characteristics of the kernel are governed by how it is excited by an input.

Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited. Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}. In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field. Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$. Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$. Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.

There are two options available to alleviate problems with aliasing. The first is to increase the spatial sampling frequency (using a higher resolution of sensors), and the second is to use wider sensors, which act like an anti-aliasing filter. The first option is more desirable, since more information is retained. In addition, if sensors are modelled as having a Gaussian pickup range than the slope of the attenuation will be gentle allowing for some low amplitude high frequency components to still be present and mild aliasing will still occur.  Mild aliasing results in distortions in the high frequency components of the field dynamics. The basis function decomposition the high frequency components are usually lost.
